Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-14 psy_peds.Rmd
Update psy_peds.Rmd

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- "2019-01-01"
history_end_date <- "2021-05-31"
pandemic_start_date <- "2020-03-15"
```

>>>>

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- "2019-01-01"
history_end_date <- "2021-08-31"
pandemic_start_date <- "2020-03-15"
```
